TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-13 paper/draft.tex
fix number

Advances in instrumentation and the lauch of several large scale spectroscopic stellar surveys launched in the past decade have dramatically increased the sample of known M dwarfs, including the \citealt{West:2011} catalog of 70,0841 sources from the Sloan Digital Sky Survey (SDSS DR7; \citealt{Abazajian:2009}), and the \citealt{Yi:2014} and \citealt{Guo:2015} catalogs of 93,619 from the Large Sky Area Multi-Object Fiber Spectroscopic Telescope (LAMOST DR1; \citealt{Zhao:2012}), which each have determined spectral subtype classifications, H$\alpha$ equivalent width, and a number of molecular band index measurements. Citations to any other large M dwarf catalogs that have

>>>>

Advances in instrumentation and the lauch of several large scale spectroscopic stellar surveys launched in the past decade have dramatically increased the sample of known M dwarfs, including the \citealt{West:2011} catalog of 70,841 sources from the Sloan Digital Sky Survey (SDSS DR7; \citealt{Abazajian:2009}), and the \citealt{Yi:2014} and \citealt{Guo:2015} catalogs of 93,619 from the Large Sky Area Multi-Object Fiber Spectroscopic Telescope (LAMOST DR1; \citealt{Zhao:2012}), which each have determined spectral subtype classifications, H$\alpha$ equivalent width, and a number of molecular band index measurements. Citations to any other large M dwarf catalogs that have
